Exploratory data analysis

### 2019-06-26 analysis/eda.Rmd
wflow_publish(knitr_in("analysis/eda.Rmd"), view = FALSE)

  fv_hr_car, fv_hr_info.gain, fv_hr_gain.ratio,
  fv_hr_symuncert, fv_hr_relief,
  fv_hr_rank, fv_hr_cor,
  fv_hr_mrmr,
  fv_hr_cmim, fv_hr_var
)
library("DataExplorer")
library("dplyr")
library("ggsci")
library("ggplot2")
```

@@

@@

>>>>

  fv_hr_car, fv_hr_info.gain, fv_hr_gain.ratio,
  fv_hr_symuncert, fv_hr_relief,
  fv_hr_rank, fv_hr_cor,
  fv_hr_mrmr,
  fv_hr_cmim, fv_hr_var,

  fv_hr_info.gain5, fv_hr_info.gain10,
  fv_hr_info.gain15, fv_hr_info.gain20,
  fv_hr_info.gain25, fv_hr_info.gain30,

  fv_vi_info.gain5, fv_vi_info.gain10,
  fv_vi_info.gain15, fv_vi_info.gain20,
  fv_vi_info.gain25, fv_vi_info.gain30,

  fv_nri_info.gain5, fv_nri_info.gain10,
  fv_nri_info.gain15, fv_nri_info.gain20,
  fv_nri_info.gain25, fv_nri_info.gain30
)
library("DataExplorer")
library("dplyr")
library("ggsci")
library("ggplot2")
```

@@

### Filter methods amongst each other

@@

### Number of bins of `FSelectorRcpp::information.gain()`

```{r}
fv_all <- dplyr::bind_rows(
  fv_vi_info.gain5$data, fv_vi_info.gain10$data,
  fv_vi_info.gain15$data, fv_vi_info.gain20$data,
  fv_vi_info.gain25$data, fv_vi_info.gain30$data
)  %>%
  dplyr::select(value, method) %>%
  mutate(id = rep(1:89, 10)) %>%
  tidyr::spread(method, value) %>%
  mutate_if(is.numeric, list(~ na_if(., -Inf))) %>% # Inf in mrmr
  na.omit() %>% 
  dplyr::select(-id)

corr <- cor(fv_all, method = "spearman")
